Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-03 draft.tex
small reshuffling

@@

\subsection{A swiss cheese model}

@@

\subsection{Koszul duality}
\label{sec: Koszul}

Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
\[
\clie \left(\fg \otimes \Omega(U) \right) .
\]

\subsection{$E_n$-calculus}
\label{sec: TT}

\bibliographystyle{alpha}  
\bibliography{centralize}

>>>>

\section{Higher calculus {\it \`a la} Kontsevich and Tamarkin-Tsygan}
\label{sec: TT}

The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $E_n$ algebra.

In Section \ref{sec:swiss} below, we will recall an elegant operadic articulation of this idea and rephrase it in terms of {\em constructible factorization algebras} on a half-space~$\HH^{n+1}$.

\subsection{Swiss cheese pairs well with centers}

Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
This $\infty$-category is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra and then taking the left-modules for this $E_1$-algebra.

@@

@@

\subsection{$E_n$-calculus}
\bibliographystyle{alpha}  
\bibliography{centralize}
